### 2016-02-12 prepReport/workPlan.tex
Corrected References

For the Python Classes, I will make use of the 3.3 version of the Python distribution, the high-performance numerical computation library Numpy\footnote{\href{http://www.numpy.org/}{http://www.numpy.org/}}, which is a standard in scientific computing, and the Matplotlib\footnote{\href{http://matplotlib.org/}{http://matplotlib.org/}} plotting library. All of this software is also free to use, and open-source. I may also need to use the PyBrain\footnote{\href{http://pybrain.org/}{http://pybrain.org/}} framework, since it has an LSTM implementation.

>>>>

For the Python implementation, I will make use of the 3.3 version of the Python distribution, the high-performance numerical computation library Numpy\footnote{\href{http://www.numpy.org/}{http://www.numpy.org/}}, which is a standard in scientific computing, and the Matplotlib\footnote{\href{http://matplotlib.org/}{http://matplotlib.org/}} plotting library. All of this software is also free to use, and open-source. I may also need to use the PyBrain\footnote{\href{http://pybrain.org/}{http://pybrain.org/}} framework, since it has an LSTM implementation.
